PM Mungbean meta-analysis

### 2019-06-21 03_Preliminary_analysis.Rmd
Updating parts of non-functional code to make functional

#### Effect of Fungicide on proportional yiTiming of fungicide application
```{r}
PM_MB_means2 <- PM_MB_means1 %>%
   filter(Fungicide == "Tebeconazole")
unique(PM_MB_means2$spray_diff)
ggplot(PM_MB_means2, aes(prop_YG))+
   geom_density(aes(fill = cut(PM_MB_means2$spray_diff, c(-1,2,7,10,12,20))), alpha = 0.5)+
   geom_vline(aes(xintercept = 0), size =0.5)+
   facet_grid(cut(PM_MB_means2$spray_diff, c(1,2,7,10,12,20))~.)+
   #scale_fill_discrete(labels = c("15-7 days before","same day","one day after","8-9 days after","13-19 days after"))+
   labs(x = "Proportion of grain yeild saved",
   title = "Grain yield proportion saved grouped by\nwhen the first fungicide application was made\nrelative to when Powdery Mildew was first seen")+
   theme(panel.grid.major = element_line(colour = "grey80"),
         panel.grid.minor = element_line(colour = "grey50"),
         panel.background = element_rect(fill = NA))+
   guides(fill=guide_legend(title="Days (binned)\nfirst spray \nwas applied\nrelative to\nFirst sign of disease"))+
   scale_x_continuous(limits = c(-0.2,0.55))
#__________________________________________________________________________________________________________
levels(factor(PM_MB_means$Fungicide))
PM_MB_means2 <- PM_MB_means1 %>%
   filter(Fungicide == "Sulphur" |
             Fungicide == "Sulphur (SC)" |
             Fungicide == "Sulphur (Ultra SC)" |
             Fungicide == "Sulphur (WP)")
unique(PM_MB_means2$spray_diff)
ggplot(PM_MB_means2, aes(prop_YG))+
   geom_density(aes(fill = cut(PM_MB_means2$spray_diff, c(-30,-19,-15,-10,-1,2,7,10,12,21))), alpha = 0.5)+
   geom_vline(aes(xintercept = 0), size =0.5)+
   facet_grid(cut(PM_MB_means2$spray_diff, c(-30,-19,-15,-10,-1,2,7,10,12,21))~.)+
   #scale_fill_discrete(labels = c("15-7 days before","same day","one day after","8-9 days after","13-19 days after"))+
   labs(x = "Proportion of grain yeild saved",
   title = "Grain yield proportion saved grouped by\nwhen the first fungicide application was made\nrelative to when Powdery Mildew was first seen")+
   theme(panel.grid.major = element_line(colour = "grey80"),
         panel.grid.minor = element_line(colour = "grey50"),
         panel.background = element_rect(fill = NA))+
   guides(fill=guide_legend(title="Days (binned)\nfirst spray \nwas applied\nrelative to\nFirst sign of disease"))+
   scale_x_continuous(limits = c(-0.3,0.6))
Chemical <- c("Amistar","Carbendazim","Tebeconazole", "propiconazole")
levels(factor(PM_MB_means$Fungicide))
for(Chem in Chemical){
PM_MB_means2 <- PM_MB_means1 %>%
   filter(Fungicide == Chem)
cat(Chem)
cat(unique(PM_MB_means2$spray_diff))
p1 <- ggplot(PM_MB_means2, aes(prop_YG))+
   geom_density(aes(fill = cut(PM_MB_means2$spray_diff, c(-50,-17,-16,-10,-9,-2.5,-2,2,2.5,9,10,16,17,30))), alpha = 0.5)+
   geom_vline(aes(xintercept = 0), size =0.5)+
   facet_grid(cut(PM_MB_means2$spray_diff, c(-50,-17,-16,-10,-9,-2.5,-2,2,2.5,9,10,16,17,30))~.)+
   #scale_fill_discrete(labels = c("15-7 days before","same day","one day after","8-9 days after","13-19 days after"))+
   labs(x = "Proportion of grain yeild saved",
   title = "Grain yield proportion saved grouped by\nwhen the first fungicide application was made\nrelative to when Powdery Mildew was first seen")+
   theme(panel.grid.major = element_line(colour = "grey80"),
         panel.grid.minor = element_line(colour = "grey50"),
         panel.background = element_rect(fill = NA))+
   guides(fill=guide_legend(title=paste(Chem,"Days (binned)\nfirst spray \nwas applied\nrelative to\nFirst sign of disease")))+
   scale_x_continuous(limits = c(-0.3,0.6))
print(p1)
Sys.sleep(10)
}
```

>>>>

```{r}
# removing 2017 and control data
# this will help look at when the first application of fungicide is applied in relation to when the disease first appeared
PM_MB_means1 <- PM_MB_means %>%
   filter(Fungicide != "control") %>%
   filter(Year != 2017) %>%
#   filter(total_Fungicide ==1) %>%
   mutate(days_from_1st = as.numeric(as.Date(as.character(Fungicide_application_1), format = "%d/%m/%Y") - 
                                        as.Date(as.character(first_sign_disease), format = "%d/%m/%Y")))

days_from_fungicid <- function(FSD,F1,F2,F3){
   dF1 <- as.numeric(as.Date(F1) - as.Date(FSD))
   dF2 <- as.numeric(as.Date(F2) - as.Date(FSD))
   dF3 <- as.numeric(as.Date(F3) - as.Date(FSD))
   if(is.na(dF1)){
      return(NA)} else{
   if(between(dF1,lower = -1, upper = 1000)){
      return(dF1)}else{
   if(is.na(dF2)){
      return(dF1)}else{
      if(between(dF2,lower = dF1, upper = -0.1)){
            return(dF2)} else{
               return(dF3)}}
            }}
}
vec1<- vector()
for(i in 1:dim(PM_MB_means1)[1]){
   dF1 <- as.numeric(as.Date(PM_MB_means1$Fungicide_application_1, format = "%d/%m/%Y")[i] -
                        as.Date(PM_MB_means1$first_sign_disease, format = "%d/%m/%Y")[i])
   dF2 <- as.numeric(as.Date(PM_MB_means1$Fungicide_application_2, format = "%d/%m/%Y")[i] -
                        as.Date(PM_MB_means1$first_sign_disease, format = "%d/%m/%Y")[i])
   dF3 <- as.numeric(as.Date(PM_MB_means1$Fungicide_application_3, format = "%d/%m/%Y")[i] -
                        as.Date(PM_MB_means1$first_sign_disease, format = "%d/%m/%Y")[i])
   if(is.na(dF1)){
      vec1 <- c(vec1,dF1)} else{
         if(between(as.numeric(dF1),-1, 1000)){
            vec1 <- c(vec1,dF1)}else{
               if(is.na(dF2)){
                  vec1 <- c(vec1,dF1)}else{
                     if(between(as.numeric(dF2),as.numeric(dF1), -1.1)){
            vec1 <- c(vec1,dF2)} else{
               if(is.na(dF3)){
                  vec1 <- c(vec1,dF2)}else{
               if(as.numeric(dF3)>=0){
                  vec1 <- c(vec1,dF2)}else{
                     vec1 <- c(vec1,dF3)}}}}
            }}
}
PM_MB_means1$spray_diff <- vec1 # gives the closest fungicide application date to the first sign of disease
#PM_MB_means1$days_from_1st

#### Effect of Fungicide 
**on proportional yield gain with repect to time of application**
##### Tebeconazole
```{r}
PM_MB_means1 %>%
   group_by(Fungicide) %>%
   filter(n() >= 5) %>% # remove any fungicide groups with less than 5 observations
   summarise(n = length(prop_YG),
             lower_2.5 = quantile(prop_YG, na.rm = T, c(0.025)),
             median = median(prop_YG, na.rm = T),
             mean = mean(prop_YG, na.rm = T),
             upper_97.5 = quantile(prop_YG, na.rm = T, c(0.975))) %>%
   kable(caption = "Fungicide effect on proportion of yield gain") %>%
   kable_styling(fixed_thead = T, full_width = T)

unique(
PM_MB_means1 %>%
   group_by(Fungicide) %>%
   filter(n() >= 5) %>%
   select(days_from_1st))

PM_MB_means1 %>%
   group_by(Fungicide) %>%
   filter(n() >= 5) %>%
ggplot(aes(prop_YG))+
   geom_density(aes(fill = cut(spray_diff, c(-1,2,7,10,12,20))), alpha = 0.5)+
   geom_vline(aes(xintercept = 0), size =0.5)+
   facet_grid(cut(spray_diff, c(1,2,7,10,12,20))~.)+
   #scale_fill_discrete(labels = c("15-7 days before","same day","one day after","8-9 days after","13-19 days after"))+
   labs(x = "Proportion of grain yeild saved",
   title = "Grain yield proportion saved grouped by\nwhen the first fungicide application was made\nrelative to when Powdery Mildew was first seen")+
   theme(panel.grid.major = element_line(colour = "grey80"),
         panel.grid.minor = element_line(colour = "grey50"),
         panel.background = element_rect(fill = NA))+
   guides(fill=guide_legend(title="Days (binned)\nfirst spray \nwas applied\nrelative to\nFirst sign of disease"))+
   scale_x_continuous(limits = c(-0.2,0.55))
#__________________________________________________________________________________________________________
levels(factor(PM_MB_means$Fungicide))
PM_MB_means2 <- PM_MB_means1 %>%
   filter(Fungicide == "Sulphur" |
             Fungicide == "Sulphur (SC)" |
             Fungicide == "Sulphur (Ultra SC)" |
             Fungicide == "Sulphur (WP)")
unique(PM_MB_means2$spray_diff)
ggplot(PM_MB_means2, aes(prop_YG))+
   geom_density(aes(fill = cut(PM_MB_means2$spray_diff, c(-30,-19,-15,-10,-1,2,7,10,12,21))), alpha = 0.5)+
   geom_vline(aes(xintercept = 0), size =0.5)+
   facet_grid(cut(PM_MB_means2$spray_diff, c(-30,-19,-15,-10,-1,2,7,10,12,21))~.)+
   #scale_fill_discrete(labels = c("15-7 days before","same day","one day after","8-9 days after","13-19 days after"))+
   labs(x = "Proportion of grain yeild saved",
   title = "Grain yield proportion saved grouped by\nwhen the first fungicide application was made\nrelative to when Powdery Mildew was first seen")+
   theme(panel.grid.major = element_line(colour = "grey80"),
         panel.grid.minor = element_line(colour = "grey50"),
         panel.background = element_rect(fill = NA))+
   guides(fill=guide_legend(title="Days (binned)\nfirst spray \nwas applied\nrelative to\nFirst sign of disease"))+
   scale_x_continuous(limits = c(-0.3,0.6))
Chemical <- c("Amistar","Carbendazim","Tebeconazole", "propiconazole")
levels(factor(PM_MB_means$Fungicide))
for(Chem in Chemical){
PM_MB_means2 <- PM_MB_means1 %>%
   filter(Fungicide == Chem)
cat(Chem)
cat(unique(PM_MB_means2$spray_diff))
p1 <- ggplot(PM_MB_means2, aes(prop_YG))+
   geom_density(aes(fill = cut(PM_MB_means2$spray_diff, c(-50,-17,-16,-10,-9,-2.5,-2,2,2.5,9,10,16,17,30))), alpha = 0.5)+
   geom_vline(aes(xintercept = 0), size =0.5)+
   facet_grid(cut(PM_MB_means2$spray_diff, c(-50,-17,-16,-10,-9,-2.5,-2,2,2.5,9,10,16,17,30))~.)+
   #scale_fill_discrete(labels = c("15-7 days before","same day","one day after","8-9 days after","13-19 days after"))+
   labs(x = "Proportion of grain yeild saved",
   title = "Grain yield proportion saved grouped by\nwhen the first fungicide application was made\nrelative to when Powdery Mildew was first seen")+
   theme(panel.grid.major = element_line(colour = "grey80"),
         panel.grid.minor = element_line(colour = "grey50"),
         panel.background = element_rect(fill = NA))+
   guides(fill=guide_legend(title=paste(Chem,"Days (binned)\nfirst spray \nwas applied\nrelative to\nFirst sign of disease")))+
   scale_x_continuous(limits = c(-0.3,0.6))
print(p1)
Sys.sleep(10)
}
```
